Data Ethics and AI

### 2024-05-28 documents/paper/paper.tex
attempt to fix Texmk error failed

Google vs DuckDuckGo | Search engine manipulation, censorship and why you should switch \citep{google-DuckDuckGo}

Google will spy on you in physical stores – Can businesses really do anything? \citep{offline-tracking-google}

>>>>

Google vs DuckDuckGo Search engine manipulation, censorship and why you should switch \citep{google-DuckDuckGo}

Google will spy on you in physical stores Can businesses really do anything? \citep{offline-tracking-google}
